Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2012-07-24 talk/icooolps2011/code/interpreter-slow.tex
ruthlessly cut space, mostly by making font smaller. not pretty, but I have no idea what to cut atm.
a slightly different approach to saving space: for the small examples, put code and trace next to each other. this makes it possible to use the larger font again.
write something about SPUR

\begin{lstlisting}[mathescape,basicstyle=\ttfamily,numbers = right]
class Class(object):
    def __init__(self, name):
        self.name = name
        self.methods = {}

@@

    def getattr(self, name):
	result = self.getfield(name)
	if result is None:
            result = self.cls.find_method(name)
	    if result is None:
		raise AttributeError
	return result
\end{lstlisting}

>>>>

{\noop
\begin{lstlisting}[mathescape,basicstyle=\ttfamily,numbers = right,numberblanklines=false]
class Class(object):
    def __init__(self, name):
        self.name = name
        self.methods = {}

@@

    def getattr(self, name):
	result = self.getfield(name)
	if result is None:
            result = self.cls.find_method(name)
	    if result is None:
		raise AttributeError
	return result
\end{lstlisting}
}
